---
title: "Stroop Effect"
author: "Enrique Araujo"
date: "July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
```

### The Stroop test

In the Stroop test, participants are given a list of words, where each is filled
with a color. The task is to say out loud the color of the word. This task in 
done in two conditions: congruent or incongruent. In the first one, the words 
are colors, and are printed in the matching color. In the second one, the word
says one color, but it's printed in another. In both cases, we measure the time 
it takes to name all the colors. Each participant records a time for each 
condition. In this exercise, the type of test is the independent variable, 
congruent or incongruent. The dependent variable is the time it takes to 
name all the colors.

### The experimental data and hypothesis

```{r}
mydata = read.csv("stroopdata.csv")
structure(mydata)
```

The data I'm using for this analysis contains results for 24 participants
over the two tasks, with the times measured in seconds. As each participant does
each task, I have *paired samples* and I'll be looking at the *pairwise 
difference* in order to draw conclusions.

Let $\mu_{C}$ be the population mean for the congruent test, and $\mu_{I}$ for
the incongruent. Their difference $\mu_{d} = \mu_{C} - \mu_{I}$ is the difference
between the population means.

Therefore, the null hypothesis $H_0$ is that the test subjects score the same
time on both tests, which means that the difference between the average
completion times for each condition $\mu_{d}$ is zero:

$$H_0: \mu_{d} = 0$$

Thus, the alternate hypothesis $H_1$ is that the type of test does affect the
outcome and the times will be different, such that the difference between the
means is not zero. The times can be better, or worse:

$$H_1: \mu_{d} \neq 0$$

### Establishing the test

The nature of the experiment and data recollection means that the most suitable
test is a **paired samples t-test**:

* Participants go through each test in the same order: first congruent, then 
incongruent. Times are recorded and are dependent. 
* We have 24 samples (low amount) for a population for which we don't know
parameters like the mean or standard deviation, and thus we will have to 
approximate them.
* We assume that the populations are normally distributed.
* Paired test means the variance of the two populations can be different and 
won't introduce errors in the test.

The test will be *two-sided*, as it's possible that a participant
scores a lower time in the second test. The paired t-test will help determine if
the conditions have a positive or negative effect on performance.

### Descriptive statistics

Before executing the test, however, first I'll take a look at some statistics 
of our data. I'll draw a summary, which includes the quantiles, median and mean,
and then calculate the standard deviation. First, the congruent task:

```{r}
summary(mydata$Congruent)
sd (mydata$Congruent)
```

In this first task, the average completion time is 14.05 seconds, with a SD of
3.559 seconds. The fastest participant completed the test more that twice as 
fast as the slowest one (8.63s vs 22.33s).

Now, I'll compute the same statistics for the incongruent task:

```{r}
summary(mydata$Incongruent)
sd(mydata$Incongruent)
```

In the second task, the average time to complete is 21.02 seconds, with a SD of
4.797 seconds. The fastest participant did it in 15.69s, with the slowest taking
a total of 35.26s.

### Distribution of sample data

```{r echo=FALSE}
plotdata = gather(mydata, key = "condition", value = "time")

ggplot(plotdata, aes(x = condition, y = time)) +
  geom_boxplot() +
  labs(title = "Box plot of times for the two tests (24 samples)",
       y = "time in seconds")
```

This is a boxplot split by the testing condition. Here it's possible
to see the clear difference in the completion time for each. Data is also quite
normally distributed, and the variance is also similar for both cases. However,
there are some possible outliers in the data for the incongruent task. 

### Executing the t-test

Finally, I calculate the t-test using R's *t.test* function. As mention before,
it's a two-sided paired test. I chose a 99% confidence interval based on the
statistics I calculated before:

```{r}
t.test(mydata$Congruent, mydata$Incongruent,
       alternative = "two.sided",
       paired=TRUE,
       conf.level = 0.99)
```

The results are clear. With a t-score of -8.0207 and a minuscule p-value, we 
reject the null hypothesis. The differing test conditions had a definite effect
on the participants performance. Subjects did noticeably worse with the 
incongruent colors, taking more time to name them, compared to the congruent
task.

### Closing remarks

The results observed show that people have more trouble naming colors when they
read a word with a different color in it. This phenomenon is known as 
interference and happens because the brain is used to reading words, like it's
automatic. So, when it's presented with a task that demands more effort, like
naming the color, it still does the reading and slows down our responses 
(Farnsworth, 2017).

Were the words in an unknown language, it's possible the participants wouldn't
be negatively affected. However, it might be interesting to perform the test on
bilingual candidates.

As this test can rate an individual's cognitive performance by using interference,
I can think of some other experiments that involve two distinct activities. For
example, a person can be told to catch colored balls and say the color out loud 
while doing it. In this case, the naming could be a distraction and might make 
the person drop some balls, or maybe the opposite can happen, and they focus on
the catching and stop naming. I think that any situation that pits an ordinary,
almost automatic task, with one that is a bit more demanding, can produce effects
like Stroop's.



#### References

Farnsworth, B., Ph.D. (2017, August 23). The Stroop Effect - How it Works
and Why. Retrieved from https://imotions.com/blog/the-stroop-effect/ 

