On the quality of red wine by Enrique Araujo
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(corrplot)
library(psych)
library(RColorBrewer)
library(gridExtra)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
mydata = read.csv("wineQualityReds.csv")
```


This dataset contains 1599 red wines alongside 11 variables that describe their
chemical properties. It provides ratings on every one on a scale from 0 
(very bad) to 10 (very excellent), agreed upon by no less than than 3 experts.

# Univariate Plots Section

First, a look at the structure of the dataset:

```{r echo=FALSE, Univariate_Plots}
str(mydata)
```

```{r echo=FALSE}
ggplot(aes(x=quality, fill=quality), data=mydata) +
  geom_bar() +
  labs(title = "Distribution of wine quality")
summary(mydata$quality)
```

The output variable of this dataset is the Quality. Most wines are middle of the
pack when it comes to quality, rating 5-6. The minimum rating is a 3, while the
maximum is 8. There are more high-rated wines than low-rated ones.

```{r echo=FALSE}
ggplot(aes(x=fixed.acidity), data=mydata) +
  geom_histogram(bins = 50) +
  labs(title = "Distribution of fixed acidity")
summary(mydata$fixed.acidity)

ggplot(aes(x=volatile.acidity), data=mydata) +
  geom_histogram(bins = 50) +
  labs(title = "Distribution of volatile acidity")
summary(mydata$volatile.acidity)

ggplot(aes(x=citric.acid), data=mydata) +
  geom_histogram(bins = 50) +
  labs(title = "Distribution of citric acid")
summary(mydata$citric.acid)
```

On one hand, the distributions for the volatile and fixed acidity are both 
similar in that they're right skewed and have a similar overall shape. Are they
correlated to each other?  On the other hand, the citric acid one is a bit more
unique, with distinct peaks at 0 and 0.50.

```{r echo=FALSE}
P1 <- ggplot(aes(x=residual.sugar), data=mydata) +
      geom_histogram(bins = 50) +
  labs(title = "Distribution of residual sugar")

P2 <- ggplot(aes(x=residual.sugar), data=mydata) +
      geom_histogram(bins = 50) +
      scale_x_log10(breaks = seq(0,16,2)) +
  labs(title = "Distribution of log10(residual sugar)")

grid.arrange(P1, P2, ncol = 1)
summary(mydata$residual.sugar)

P1 <- ggplot(aes(x=chlorides), data=mydata) +
      geom_histogram(bins = 50) +
  labs(title = "Distribution of chlorides")

P2 <- ggplot(aes(x=chlorides), data=mydata) +
      geom_histogram(bins = 50) +
      scale_x_log10(breaks = seq(0,1,0.1)) +
  labs(title = "Distribution of log10(chlorides)")

grid.arrange(P1, P2, ncol = 1)
summary(mydata$chlorides)
```

Looking at the residual sugar and chlorides (salts), both variables have similar
right-skewed distributions. Most wines have quite similar values: between 2 and
3 for sugar, and 0.1 to 0.2 for chlorides. 

Tranforming the scales gives a closer look.Since there are no 0 values I used a 
log10 transform on the x-axis. Like this, distributions are well behaved and 
have a clear mode. Since these two data had very noticeable outliers, I'm 
curious about the quality of the wines to which these belong to, especially the 
sweeter wines, so I'll subset them:

```{r echo=FALSE}
ggplot(aes(x=quality), data=subset(mydata, residual.sugar > 10)) +
  geom_bar() + labs(title = "Distribution of quality of sweet wines")
```

I plotted the quality of wines that have more than 10 grams per liter of sugar.
Not only do we have few fines that satisfy this condition, but their quality
doesn't go beyond a 6.

```{r echo=FALSE}
P1 <- ggplot(aes(x=free.sulfur.dioxide), data=mydata) +
  geom_histogram(binwidth = 2) +
  labs(title = "Distribution of free SO2")

P2 <- ggplot(aes(x=free.sulfur.dioxide), data=mydata) +
  geom_histogram(bins = 50) +
  scale_x_log10(breaks = c(2,4,6,8,10,15,20, 40, 60)) +
  labs(title = "Distribution of log10(free SO2)")

grid.arrange(P1,P2,ncol = 1)
summary(mydata$free.sulfur.dioxide)

P1 <- ggplot(aes(x=total.sulfur.dioxide), data=mydata) +
  geom_histogram(binwidth = 5) +
  labs(title = "Distribution of total SO2")

P2 <- ggplot(aes(x=total.sulfur.dioxide), data=mydata) +
  geom_histogram(bins = 50) +
  scale_x_log10(breaks = c(10,20,30,40,50,100,200)) +
  labs(title = "Distribution of log10(total SO2)")

grid.arrange(P1,P2,ncol = 1)
summary(mydata$total.sulfur.dioxide)

ggplot(aes(x=sulphates), data=mydata) +
  geom_histogram(bins = 75) +
  coord_cartesian(xlim = c(0,quantile(mydata$sulphates,0.99))) +
  labs(title = "Distribution of sulphates")

summary(mydata$sulphates)
```


This next trio of variables have a similar pattern. They're right-skewed, which
means the majority of the wines have similar quantities of chemicals and there
are a few outliers which drive the means up. Once again, I use a log-transform
on the first two to get a closer look. For the sulphates, I limit the x-axis to 
show up to the 99th percentile.

With the transformation I see that the free and total SO2 distributions are 
not what the seemed to be. Data points are more  interspersed in the lower 
values for the free SO2, with the mode being around 6, with another peak near 16.
On the other hand, for the total SO2, values seem normally distributed on a log
scale. The mode is between 40 and 50.

```{r}
length(subset(mydata, free.sulfur.dioxide > 50))
```

It is said that free sulfur dioxide, in concentrations of over 50ppm (mg/L), 
becomes evident in the nose and taste of wine. So I look at the quality of the 
13 wines that go over this concentration.

```{r echo=FALSE}
ggplot(aes(x=quality), data=subset(mydata, free.sulfur.dioxide > 50)) +
  geom_bar() + labs(title = "Quality of wines with high free SO2")
```

Since there are few wines with high concentrations of free SO2 it's difficult
to draw conclusions. Nonetheless, it's curious that these wines have scores of
5 to 7, as high concentrations can be seen as negatives beforehand. In this case
it appears that it doesn't have much of a negative impact, we even find that
there are two wines with a score of 7.

```{r echo=FALSE}
ggplot(aes(x=density), data=mydata) +
  geom_histogram(bins = 75) +
  labs(title = "Distribution of wine density")
summary(mydata$density)

ggplot(aes(x=pH), data=mydata) +
  geom_histogram(bins = 60) +
  labs(title = "Distribution of pH")
summary(mydata$pH)

ggplot(aes(x=alcohol), data=mydata) +
  geom_histogram(bins = 60) +
  labs(title = "Distribution of alcohol")
summary(mydata$alcohol)
```

The final 3 variables. Density and pH are the first chemical variables to not be
skewed. Density might not be that important to quality, by definition it's 
mostly dependent on the concentration of other chemicals and has very little 
range (in g/ml):

```{r}
max(mydata$density) - min(mydata$density)
```

Alcohol and pH, however, have much wider ranges and might have something to say 
about the flavor of the wine. 

# Univariate Analysis

### What is the structure of your dataset?

There are 1599 wines in this dataset with 12 features:  

 1.   fixed acidity 
 2.   volatile acidity 
 3.   citric acid 
 4.   residual sugar 
 5.   chlorides 
 6.   free sulfur dioxide 
 7.   total sulfur dioxide 
 8.   density 
 9.   pH
 10. sulphates 
 11. alcohol
 12. quality 

All variables except for quality are decimal numbers which describe a chemical
property of the wine. Quality is an integer between 0 and 10. Most wines have
a quality of 5 or 6. Also, we don't have any 9's or 10's in this data.

### What is/are the main feature(s) of interest in your dataset?

The main feature of interest in this dataset is the quality of the wine. I'd like
to learn which of the chemicals variables are most closely related to the taste
and score.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

I think the most important features are the ones that are closely related to the
taste, according to the dataset's description. These variables are the volatile
acidity, which if high can lead to an unpleasant vinegar-like taste; the citric
acid concentration, which is said to be related to 'freshness' and flavor; the 
chlorides, which is the concentration of salts; and the sulphates, which are an
additive that controls microbial growth and affects the SO2 concentration, 
affecting taste indirectly.

### Did you create any new variables from existing variables in the dataset?

I did not create any new variables during the past section.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

Most distributions were right-skewed, and some variables, like sulphates, 
chlorides and residual sugar, had more outliers than the others. The citric acid
distribution has two spikes, one at zero and one near 0.5. However I did not see
the need to change the form of the data or use log scales in the histograms.

# Bivariate Plots Section

```{r echo=FALSE, Bivariate_Plots}
M <- cor(subset(mydata, select = -c(X)))
corrplot(M, method = "ellipse")
```

First, since I have so many variables with long names, I create a plot with the
correlation ellipses between them. Already we see some strong relationships. 
Some are expected, like pH being more acidic on wines with more citric acids and
fixed acidity. And some are curious, like the one relationship between alcohol 
and quality.

Since I'm looking at quality as the main output feature, I'll look into the 
variables with the most correlation next, beginning with the positive.

```{r echo=FALSE}
pairs.panels(subset(mydata, select = c(quality, alcohol,
                                       sulphates, citric.acid)), 
              method = "pearson", 
              hist.col = "#00AFBB",
              density = TRUE,  
              ellipses = TRUE
)
```

These are the variables with the most positive correlation to the quality. 
Still, it's a moderate correlation at best. Now, for the negatively correlated 
ones.

```{r echo=FALSE}
pairs.panels(subset(mydata, select = c(quality, volatile.acidity,
                                       density, total.sulfur.dioxide)), 
              method = "pearson", 
              hist.col = "#00AFBB",
              density = TRUE,  
              ellipses = TRUE 
)
```

According to the dataset's descriptions, some variables with considerable
correlation do affect the flavor of the wine directly:  

*   Volatile acidity - Is unpleasant when high; tastes like vinegar.  
*   Citric acid - Adds 'freshness' to the wine.

The other two, alcohol and sulphates, have different effects. Alcohol is alcohol,
while the sulphates [help preserve the freshness by
preventing oxidation](https://www.thekitchn.com/the-truth-about-sulfites-in-wine
-myths-of-red-wine-headaches-100878). This means the sulphates are related to 
a wine's shelf life.

Next, for a deeper look at the variables, I group them by the quality of the 
wine to see how they vary.

```{r echo=FALSE}
ggplot(data = mydata, aes(factor(quality), volatile.acidity)) +
  geom_boxplot() + 
  labs(tile = "Volatile acidity vs quality boxplot")

#by(mydata$volatile.acidity, mydata$quality, summary)
```

This box-plot showcases how different are the higher rated wines from the poor
ones. In terms of volatile acidity, most of the wines rated 7 or 8 have less
than 0.5g/L of acetic acid. Poor rated wines, on the contrary, have a 
concentration of more than 0.6g/L. This is in line with the descriptions,
poorly rated wines have unpleasant taste.

```{r echo=FALSE}
ggplot(data = mydata, aes(factor(quality), citric.acid)) +
  geom_boxplot()  +
  labs(tile = "Citric acid vs quality boxplot")

#by(mydata$citric.acid, mydata$quality, summary)
```

Next up is the concentration of citric acid. In this one the most noticeable 
feature is the variance, which is large for ratings 3 to 6, but small for wines
rated 7-8. Most top rated wines have more than 0.3g/L of citric acid. There is 
a moderate, positive relationship between this and the flavor. Critics tend to
like wines with more citric acid, although is not the only factor.

```{r echo=FALSE}
ggplot(data = mydata, aes(factor(quality), alcohol)) +
  geom_boxplot() +
  labs(tile = "Alcohol vs quality boxplot")

#by(mydata$alcohol, mydata$quality, summary)
```

Now this one is a relationship I didn't not expect, yet the data shows that it's
not by mere chance. Many top rated wines are firmly above the 11% mark, while
the worst ones (rated 3) are below it. Surely, having more alcohol does not make
a better wine, but the worse wines have little of it.

```{r echo=FALSE}
ggplot(data = mydata, aes(factor(quality), sulphates)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0.25,1.25)) +
  labs(tile = "Sulphates vs quality boxplot")

#by(mydata$sulphates, mydata$quality, summary)
```

Finally, the concentration of sulphates. High-rated wines tend to have more 
sulphates in a tendency similar to the last two variables. It's hard to relate 
this variable to the wine's flavor without taking into account its shelf life.
It could be that the poorer wine's taste worsens quicker.

Now, looking outside of quality, I see other strong relationships, like pH and
fixed acidity, and alcohol and density. These have very clear scientific 
explanations, but nonetheless it'll be interesting to take a look at them
in plots.

```{r echo=FALSE}
ggplot(aes(x=fixed.acidity, y=pH, alpha = 1/100), data = mydata) +
  geom_point() +
  geom_smooth(method = "lm") + 
  theme(legend.position="none") +
  labs(tile = "pH vs fixed acidity")
```

First, the acidity. More acids lower the pH, as is expected, and that shows in
the r values for these two variables. Of course, pH is also affected by other 
variables, like citric acid concentration and alcohol percentage. This shows in
the variability of the points in this plot.

```{r echo=FALSE}
ggplot(aes(x=alcohol, y=density, alpha = 1/100), data = mydata) +
  geom_point() +
  geom_smooth(method = "lm") + 
  theme(legend.position="none") +
  labs(tile = "density vs alcohol")
```

Next up, alcohol and density. Because, alcohol is less dense than water 
(density = 1), more alcohol content means less density, which explains the 
correlation. However, much like in the pH's case, other variables have an effect
on the density, since they are the concentration of chemicals present in the 
wine. I think it's safe to say many of the chemical variables are correlated
in one way or another.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

The quality of a wine varies a bit with other features, such as the concentration
of citric acid, sulphates and acetic acid (volatile acidity), and also has a
moderate correlation with the alcohol percentage. All these relationships are 
weak, however, between coefficients of 0.2 and 0.4.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

The relationships between the other variables have clear scientific foundations
yet are interesting to see. The concentration of acids (citric, acetic) have a 
clear effect on the density and pH; more acids, more density and lower pH. 
Alcohol is also related like this, as wines with more alcoholic content 
tend to have lower pH and less density, as is expected.

### What was the strongest relationship you found?

The strongest relationship according to Pearson's coefficient is pH and fixed
acidity, with a value of -0.6829. This means the concentration of tartaric acid
explains at least 68% of the variation in pH across our wine data.

# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}
ggplot(mydata, aes(sulphates,
                   color=factor(quality),
                   fill = factor(quality))) +
  geom_density(alpha = 0.4) +
  coord_cartesian(xlim = c(0.3,1.3)) +
  scale_fill_brewer() + scale_color_brewer() + theme_dark() +
  labs(title = "Sulphate density")

ggplot(mydata, aes(alcohol,
                   color=factor(quality),
                   fill = factor(quality))) +
  geom_density(alpha = 0.4) +
  scale_fill_brewer() + scale_color_brewer() + theme_dark() +
  labs(title = "Alcohol density")

ggplot(mydata, aes(citric.acid,
                   color=factor(quality),
                   fill = factor(quality))) +
  geom_density(alpha = 0.4) +
  scale_fill_brewer() + scale_color_brewer() + theme_dark() +
  labs(title = "Citric acid density")

ggplot(mydata, aes(volatile.acidity,
                   color=factor(quality),
                   fill = factor(quality))) +
  geom_density(alpha = 0.4) +
  scale_fill_brewer() + scale_color_brewer() + theme_dark() +
  labs(title = "Volatile acidity density")
```

These density plots expand upon the relationships showcased in the previous 
boxplots. These 4 variables are the ones with the strongest correlation to the
quality, and in these plots we can see the attributes of the best wines more
clearly.

The two chemical quantities that stand out the most are sulphates and volatile
acidity. The majority of high quality wines (rated 7-8) are on a class apart 
from the rest: they have more sulphates and less acetic acid (volatile acidity)
and it clearly shows in the density plots.

The other two variables, citric acid and alcohol, don't show clear differences.
In addition, it's important the ranges of these distributions. Higher quality 
wines tend to have distinct quantities of chemicals, yet there are some high 
quality wines that have few sulphates or citric acid, or somewhat elevated
volatile acidity.

```{r echo=FALSE}
ggplot(aes(sulphates, volatile.acidity, color=factor(quality)), data=mydata) +
  geom_point() +
  coord_trans(x = 'log', y = 'log') +
  scale_color_brewer() + theme_dark() +
  labs(title = "Volatile acidity vs sulphates")
```

Now, to look further into these relationships, I plot two variables against
each other on a scatter plot, coloring each point by the wine's quality. In this 
first one I pitted the volatile acidity against the sulfate concentration. Data
points are very scattered but there is a noticeable pattern in there. Since the 
higher values are outliers, I use a log transform in the x-axis.

```{r echo=FALSE}
ggplot(aes(sulphates, volatile.acidity, color=factor(quality)), data=mydata) +
  geom_point() +
  coord_trans(x = 'log', y = 'log') +
  scale_color_brewer() + theme_dark() +
  facet_wrap(~factor(quality)) +
  labs(title = "Volatile acidity vs sulphates (Faceted)")
```

Faceting this scatter plot makes us appreciate how little data we have for 
wines rated 3 and 8. We can a moderate relationship between these variables: 
worse wines are up to the left, while the better ones are centered in the plot.
This time I use a log transform for the sulphates, and a square root transform
for the citric acid, which has 0 values.

```{r echo=FALSE}
ggplot(aes(sulphates, citric.acid, color=factor(quality)), data=mydata) +
  geom_point() +
  coord_trans(x = 'log', y = 'sqrt') +
  scale_color_brewer(palette = "Purples") + theme_dark() +
  labs(title = "Citric acid vs sulphates")
```

My second plot has citric acid vs sulphates. These two have moderate positive
correlation to quality, so it's expected that higher values for each means a
better wine. However, we see a lot of variation in here as fell. Once again, I 
use a log transform for the x-axis and square root for y-axis.

```{r echo=FALSE}
CV <- ggplot(aes(volatile.acidity, citric.acid, color=factor(quality)), data=mydata) +
  geom_point() +
  coord_trans(x = 'log', y = 'sqrt')  +
  scale_color_brewer(palette = "Oranges") + theme_dark() +
  labs(title = "Citric acid vs volatile acidity")

CV
```

Finally, I compare two acids, citric vs acetic. One is related with fresh taste,
the other with a bad, vinegar-like one. Once again, there is a lot of variance.

```{r message=FALSE, warning=FALSE}
CV + facet_wrap(~cut(sulphates, c(0,0.5,0.6,0.7,0.8,0.9,2))) +
  scale_color_brewer(palette = "Reds") +
  labs(title = "Citric acid vs volatile acidity (faceted)")
```

In an effort to integrate another variable into this scatterplot, I tried 
faceting by the amount of sulphates. I defined bins that tried to divide the
data points into something that made sense. The result shows how the majority
of wines, which are rated 5-6, are in the first 3 bins, from 0 to 0.7 g/L of 
potassium sulphate. The next two bins are dominated by the better wines, and 
the final one is filled with outliers and has wines of every rating.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

First, the volatile acidity is bad for the taste when it's high, so poorer wines
tend to hang out in the upper values. The sulphates appear to have a positive
relationship with quality, and the best wines are centered around a
value of 0.8, yet with high variance.

Wines rated 8 points can have little citric acid or a lot. There seems to be a 
'sweet spot' in which the high quality wines are, as too much citric acid seems
to be disliked.

Comparing citric and acetic acid, the best wines tend to have little volatile 
acidity and a good amount of citric acid. It appears there's a weak negative 
correlation between these two. Note that the worse wines tend to have more 
acetic acid, yet there are some outliers within the high scores that do too.

### Were there any interesting or surprising interactions between features?

I'm most surprised at how there is so much variance in the data. It's easy to 
find where the bad ones will be, but the good ones appear all over the plots.
Since the correlations are not that strong, it's very difficult to build a model
that can predict the score by looking a these variables. If I did build one, I'd
certainly expect it to be better at classifying bad wines. There are many 
outliers, it's possible to find a bad wine that has two or three properties
on the same level as a good one.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(mydata, aes(citric.acid,
                   color=factor(quality),
                   fill = factor(quality))) +
  scale_fill_brewer(palette = 'Oranges') +
  scale_color_brewer(palette = 'Reds') +
  theme_dark() + labs(x = "citric acid (g / dm^3)",
                      title = "Citric Acid") + 
  geom_density(alpha = 0.4)
```

### Description One

The distribution of the concentration of citric acid is the most unique one. It
has these spikes at 0 and 0.5 g/L while being otherwise unremarkable. As the 
presence of citric acid is desirable, the density plots per wine quality gives
an alternate view of this distribution, and show that most of the wines with no
citric acid have poor taste. Wines rated 7 and 8 have a considerable number of
samples with concentrations around 0.5g/L.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(data = mydata, aes(factor(quality), y = volatile.acidity)) +
  geom_violin() +
  theme_dark() + labs(x = "Wine Quality",
                      y = "Acetic acid - g / dm^3",
                      title = "Volatile Acidity") + 
  theme(legend.position="none")
```

### Description Two

Volatile acidity, also known as the concentration of acetic acid, is the
variable that has the strongest negative correlation with quality. Too much
acetic acid can make for very bad taste. The boxplot and the density plot we did
for this variable showcased this relationship well, so the violin plot is a nice
combination of the two. The best wines have a distribution that leans towards 
low quantities of acetic acid. However, this quantity alone can't determine
how good a wine is.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(sulphates, volatile.acidity, color=factor(quality)), data=mydata) +
  geom_point(alpha = 0.3) +
  coord_trans(x = 'log', y = 'log') +
  scale_color_brewer(palette = 'Reds') + theme_dark() +
  labs(x = "potassium sulphate - g / dm^3",
       y = "Acetic acid - g / dm^3",
       title = "Volatile Acidity vs. Sulphates by quality") + 
  facet_wrap(~factor(quality)) + 
  theme(legend.position="none")
```

### Description Three

This plot highlights how difficult it can be to separate the best wines from the 
worst based on chemical qualities. The volatile acidity and the sulphates were
two variables that, in density plots, separated the top wines more clearly. Yet,
when put together in a scatterplot, the separation definitely isn't as clear. 
Better wines appear to be a subset of the previous rating. There is no clear
linear relationship between quality and other variables.

------

# Reflection


This red wine dataset contained information on 1599 wines, with measurements
for 11 chemical properties and one output variable: quality. I began by plotting
the distributions of each variable, and then looked for relationships using
pearson's correlation coefficient. Once I had identified the most useful
variables, I plotted two and three-variable graphics which could help visualize
how they were related to the quality more effectively.

To my surprise, there wasn't a clear-cut relationship between the many
chemical properties and a wine's quality. Nowhere I could draw a line and say 
"that's it, from this point on there are only high quality wines". In spite of
this, I managed to observe some interesting relationships, like the ones between
sulphates and citric acid with a wine's quality.

I think the main limitation of this dataset lies in the quantity of observations.
There are 1599 wines, yet too few of them are rated 3 or 8, and we even lack 
wines rated more than 8, or less than 3. Correlations are moderate at best, so
it's difficult to build models that predict a wine's quality according to these
variables. I feel that with more data points, a reliable, more complex model can
be built, perhaps with some machine learning algorithm.